---
title: "Summary of videos"
format: html
---

# TikTok Video View Summary
This report provides an overview of the TikTok video view dataset and summarizes several key performance indicators.

## 1. Load the Data
```{r}
library(tidyverse)
library(here)
videos <- read.csv(here("data", "raw", "video_view.csv"))
```
Due to the folder structure, we have to make use of the "here" package so that the file runs both normally and when it is rendered
## 2. Dataset Overview
```{r}
head(videos)
glimpse(videos)
```
This section provides a first look at the structure and contents of the dataset.

## 3. Missing Values Check
```{r}
videos %>%
  summarise(
    missing_watch_rate = sum(is.na(watch_rate)),
    missing_impressions = sum(is.na(impressions_n))
  )
```
This check shows whether missing values are present in the main variables used in the analysis.

## 4. Summary Statistics
```{r}
videos %>%
  summarise(
    number_of_videos = n(),
    total_impressions = sum(impressions_n, na.rm = TRUE),
    average_watch_rate = mean(watch_rate, na.rm = TRUE)
  )
```
These summary statistics provide an overview of the number of videos, total impressions, and average watch rate in the dataset.

## 5. Creator Summary
```{r}
creator_summary <- videos %>%
  group_by(creator_id) %>%
  summarise(
    videos_n = n(),
    impressions_total = sum(impressions_n, na.rm = TRUE),
    watch_rate_avg = mean(watch_rate, na.rm = TRUE)
  ) %>%
  arrange(desc(impressions_total))

creator_summary
```
The creator summary compares creators based on their number of videos, total impressions, and average watch rate.

## 6. Top 5 Videos by Impressions
```{r}
videos %>%
  arrange(desc(impressions_n)) %>%
  select(video_id, creator_id, impressions_n, watch_rate) %>%
  head(5)
```
This table identifies the five videos with the highest number of impressions.

## 7. Publishing Date Analysis
```{r} 
arranged_date <- videos %>% 
    mutate(publishing_date = as.POSIXct(published_at, origin = "1970-01-01", tz = "CET")) %>%
    select(creator_id, video_id, publishing_date, watch_rate) %>% 
    arrange(desc(publishing_date))
head(arranged_date, 20)
```
The above code shows the earliest 20 videos inside of the dataset and their corresponding dates, derived from the UNIX code. It assumes that the UNIX seconds are recorded in accordance with the CET timezone

## Time Between Impressions Analysis
```{r}
time_between_impressions <- videos %>% 
    filter(!is.na(first_impression_at)) %>% 
    filter(!is.na(last_impression_at)) %>% 
    mutate(time_between_first_and_last_impression = last_impression_at - first_impression_at) %>% 
    mutate(hours_between_first_and_last_impression = time_between_first_and_last_impression / 3600) %>%
    mutate(days_between_first_and_last_impression = hours_between_first_and_last_impression / 24) %>% 
    select(creator_id, video_id, impressions_n, days_between_first_and_last_impression, hours_between_first_and_last_impression) %>%
    arrange(desc(hours_between_first_and_last_impression))
head(time_between_impressions) 
```
The above code first filters out videos with missing values for first and last impressions, then calculates the difference between the two, transforms this into hours and days, and finally arranges from largest gap between impressions to the smallest gap between first and last impressions.

# Conclusion
The analysis provides a general overview of the dataset, checks for missing values, summarizes overall performance, compares creators, and identifies the videos with the highest number of impressions.