---
title: "Visual Analysis of Tiktok Sessions Dataset"
format: html
---
# TikTok Sessions Visual Analysis
This report provides a visual overview of the TikTok Sessions dataset using several key performance indicators.


## 1. Download The Needed Packages
```{r}
library(tidyverse)
library(here)
library(ggplot2)
```
For this analysis, the following packages are needed: 1. tidyverse, 2. ggplot2, 3. here

### 2. Loading The Data

```{r}
sessions <- read.csv(here("data", "data_session", "sessions.csv"))
head(sessions)
dim(sessions)
summary(sessions)
```
It shows that the sessions datafile consists of only 7 columns, but almost 100,000 rows of data

### 3. Checking


### 4. Removing Rows with Missing Data for Critical Variables

```{r}
missing_data <- sessions %>% 
    select(session_duration_sec, videos_viewed, watch_seconds) %>% 
    summarise(across(everything (),
    list(missing = ~sum(is.na(.)))
    ))

missing_data
```
So, according to this code, the three key numeric data columns do not have any missing data

### 4.